tSZ $\times$ galaxies

### 2019-04-04 notes/notes.tex

>>>>

\newpage
\section{Next steps}
\begin{itemize}
  \item Systematics in $gg$. We could try deprojection and see if things improve. Otherwise just remove first point or two in WISC data.
  \item Systematics in $gy$: quantify CIB contamination.
  \item Do we want a different angle on the signal modelling? E.g.:
        \begin{enumerate}
          \item Our measurement could be transformed into a measurement of the mean electron pressure weighed by halo bias at a given redshift:
                \begin{equation}
                  \bar{P}_{e,b}(z) = \int dM\,\frac{dn}{dM}\,b_h(M) \bar{P}_e(M,z)
                \end{equation}
          \item We could quantify whether there's any statistical evidence for a redshift evolution of $1-b_H$.
          \item $\rho_{gy}\simeq-0.5$. Is there anything we can say about that?
        \end{enumerate}
\end{itemize}
